---
title: "R Markdown and Plotly"
author: "Di Zhu"
date: "2/15/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Instructions

- Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. 

- Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Review Criteria

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

- Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## Set up The Environment

```{r, echo = TRUE, message = FALSE}
library(quantmod)
library(dplyr)
library(tidyr)
library(plotly)
```

## Load The Stock Data

```{r, echo = TRUE, message = FALSE, results = 'hide'}
from.dat <- as.Date("01/01/20", format = "%m/%d/%y")
to.dat <- as.Date("12/31/20", format = "%m/%d/%y")
getSymbols("GOOG", src = "yahoo", from = from.dat, to = to.dat)
getSymbols("TSLA", src = "yahoo", from = from.dat, to = to.dat)
getSymbols("AAPL", src = "yahoo", from = from.dat, to = to.dat)
getSymbols("FB", src = "yahoo", from = from.dat, to = to.dat)

stocks = data.frame(goog = GOOG$GOOG.Close, tsla = TSLA$TSLA.Close, 
                    aapl = AAPL$AAPL.Close, fb = FB$FB.Close)
date = rownames(stocks)
stocks = cbind(date = date, stocks)
rownames(stocks) = 1: nrow(stocks)
```

## Pivot Data and Create The Plot

```{r, echo = TRUE}
stocksPivot = stocks %>%
      rename(GOOG = GOOG.Close, TSLA = TSLA.Close, 
             AAPL = AAPL.Close, FB = FB.Close) %>%
      pivot_longer(!date, names_to = 'index', values_to = 'price')
stocksPivot$date = as.POSIXct(stocksPivot$date)

fig = plot_ly(stocksPivot, x = ~date, y = ~price, color = ~index, 
              type = "scatter", mode = "lines")
fig = fig %>%
      layout(title = 'Stock Price of 4 Big Tech Companies in 2020', 
             xaxis = list(title = 'Date'), 
             yaxis = list(title = 'Close Price ($)'))
```

***

```{r}
fig
```


