---
title: "R Markdown and Leaflet"
author: "Di Zhu"
date: "2/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Instructions

Create a web page using R Markdown that features a map created with Leaflet. Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. 

### Review criteria

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Does the web page feature an interactive map that appears to have been created with Leaflet?

### Executive Summary

The top 10 most populated cities in the United States as of 2020 are marked on the map with circles on each city proportional to the population of that city. 

The population data comes from the website: https://worldpopulationreview.com/us-cities

The latitude and longitude data comes from the website: https://www.latlong.net/country/united-states-236.html

### Load the data

```{r}
popData = data.frame(city = c('New York City, NY', 'Los Angeles, CA', 'Chicago, IL', 'Houston, TX', 'Phoenix, AZ', 'Philadelphia, PA', 'San Antonio, TX', 'San Diego, CA', 'Dallas, TX', 'San Jose, CA'), 
                     pop = c(8622357, 4085014, 2670406, 2378146, 1743469, 1590402, 1579504, 1469490, 1400337, 1036242), 
                     lat = c(40.730610, 34.052235, 41.881832, 29.749907, 33.448376, 39.952583, 29.424349, 32.715736, 32.779167, 37.335480), 
                     lng = c(-73.935242, -118.243683, -87.623177, -95.358421, -112.074036, -75.165222, -98.491142, -117.161087, -96.808891, -121.893028))

popData$hover = with(popData, paste(city, '<br>', 'Population: ', pop))
```

### Leaflet Map

```{r}
library(leaflet)
popData %>% 
      leaflet() %>%
      addTiles() %>%
      addCircles(weight = 1, radius = sqrt(popData$pop)*50, popup = popData$hover)
```


